{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-04-25 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

    % =================================================

@@

    % ==================================================

@@

            % ==========================================================================================================

@@

            % ==========================================================================================================

@@

                    \item The quadratic growth condition with $\mathbb F(L_f, \kappa_f)$. No convexity is needed. 

@@

                \textbf{Firstly, we show that QFG implies PEB.}
                Consider \eqref{ineq:proj-grad} with $z = x^+_\Pi$ it yields: 

@@

                    \quad&\underset{\text{(ii)}}{\ge }

@@

                Skipping algebra, the fraction simplifies to 

>>>>

    % ==========================================================================

@@

    % ==========================================================================

@@

            % LEMMA | QFG AND GRADIENT MAPPING
            \begin{lemma}[gradient mapping and quadratic function growth]\;\label{lemma:grad-map-qfg}\\
                Let $f$ satisfies Assumtion \ref{ass:necoara-2019-settings}. 
                Suppose that $f \in \mathbb F(L_f, \mu_f, X)$ so it satisfies the quadratic function growth condition. 
                For all $x \in \RR^n$, define $x^+ = \Pi_X(x - L^{-1}_f\nabla f(x))$, 
                definte projections onto the set of minimizers $x^+_\Pi = \Pi_{X^+} x^+, X_\Pi = \Pi_{X^+}x$, then
                    \right)\Vert x^+ - x_\Pi^+\Vert
                    &\le \Vert L_f(x - x^+)\Vert. 
                Using convexity, consider \eqref{ineq:proj-grad} with $z = x^+_\Pi$ it yields: 
                    - \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - x^+_\Pi\Vert.

@@

@@

@@

                Starting with Lemma \ref{lemma:grad-map-qfg} because $f$ satisfies quadratic growth and it is assumed convex, then it has: 

@@

@@

                Skipping some algebra, the fraction simplifies to 
